Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-02-19 strang/paper.tex
update text

We are using Castro

\section{Simulations}

\subsection{Reacting convergence test problem}

We use the reacting convergence test problem introduced in \cite{castro_sdc}.

>>>>

We are using the freely-available \castro\ simulation
code~\citep{castro,castro_joss}.  \castro\ solves the equations of
hydrodynamics using an unsplit piecewise parabolic method coupled with
gravity and reactions.  For reactive flow, either Strang splitting or
spectral deferred corrections are used to couple the hydrodynamics and
reactions~\citep{castro_sdc}.  Here we focus on the Strang splitting.

One option to make temperature integration less expensive is to freeze
the values of the thermodynamics quantities at the start of the
reactive integration.  This approach was done in \citet{ABNZ:III}.
This can work well in ``simmering'' phases of reactions where the
thermodynamic state is not changing much over a timestep, but for
explosive reactions, this may be a poor approximation.

In \cite{castro_sdc}, we introduced a test problem where we could
measure the convergence of a reacting hydrodynamics problem via
Richardson extrapolation---this was an acoustic pulse with helium
burning via $3-\alpha$ and
$\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$.  Those tests focused on
SDC coupling and showed that we can get overall 4th order in space and
time convergence.  Here we run the same test with Strang coupling,
looking at the various approaches at incorporating a temperature
equation in the reactive portion of the update.
